 

### 2021-07-12 vertical-thermal-review.Rmd
moved deciduousness text from traits to ecology

**Differences across forest vertical gradients in biophysical conditions, plant traits, and metabolism scale up to affect whole-tree ecology, ecosystem ecology, and their thermal sensitivity (Fig. `r fig_schematic`).** 
Vertical gradients in the biophysical environment shape which plant strategies, or sets of traits, are competitive in canopy versus understory conditions, thereby

>>>>

**Differences across forest vertical gradients in biophysical conditions, plant traits, and metabolism scale up to affect community composition, whole-tree ecology, and ecosystem ecology (Fig. `r fig_schematic`).**

### Size-structuring of communities

Vertical gradients in the biophysical environment shape which plant strategies, or sets of traits, are competitive in canopy versus understory conditions, thereby shaping community composition across size classes.
